---
title: "Proejct1_data607"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r }
library(RCurl)
library(data.table)
library(tidyr)
library(readr)
library(stringr)
library(dplyr)
```

## Read the text files 

```{r }
lines<-read_lines("F:\\CUNY masters\\project1_data_607\\7645617.txt")
lines[1:10]
```
## Creating two data frames with player data and round data from text_file

```{r }
chess_player<-c()
chess_round<-c()

 for (i in seq(5, 195, 3)) {
  row5 <- unlist(strsplit(lines[i], '\\|'))
  player_num <- as.numeric(gsub(' ', '', row5[1]))
  player_name <- str_trim(row5[2])
  total_point <- str_trim(row5[3])
  
  row6 <- unlist(strsplit(lines[i+1], '\\|'))
  player_state <- str_trim(row6[1])
  player_pre_rating <- unlist(str_extract_all(row6[2], "[[:digit:]]+"))[2]
  
  chess_player<- rbind(chess_player, c(player_num, player_name, player_state, total_point, player_pre_rating))
  df1 <- data.frame(row5[4:10])
  df1$player_num <- player_num
  df1$player_pre_rating <- player_pre_rating
  
  chess_round<- rbind(chess_round,df1)
}
```

## Get the player data into a data frame

```{r }

df2 <- data.frame(chess_player)
colnames(df2) <- c("player_num", "player_name", "player_state", "total_point", "player_pre_rating")
head(df2)
```
## Get the round data into a data frame by doing some string cleaning and data conversion. 

```{r }
colnames(chess_round) <- c("win_loss_opponent_id", "player_num", "player_pre_rating")
chess_round$win_loss <- sapply(strsplit(as.character(chess_round$win_loss_opponent_id), ' '), '[', 1)
chess_round$opponent_id <- sapply(chess_round$win_loss_opponent_id, function(x)gsub('\\s+', ' ', x))
chess_round$opponent_id <- as.numeric(sapply(strsplit(as.character(chess_round$opponent_id), ' '), '[', 2))
chess_round$player_pre_rating <- as.numeric(chess_round$player_pre_rating)
chess_round<- chess_round[, c('player_num', 'win_loss', 'opponent_id', 'player_pre_rating')]
head(chess_round)
```

## Calculating average and merging player and round data frame into one data frame 

```{r }

col_01 <- c('player_name', 'player_state', 'total_point', 'player_pre_rating', 'avg')
avg_pre <- chess_round%>% group_by(opponent_id) %>% summarise(avg = as.integer(mean(player_pre_rating)), .groups='drop')

df2 <- merge(df2, avg_pre, by.x="player_num", by.y="opponent_id")[, col_01]
df2$total_point<-as.numeric(df2$total_point)
head(df2)
```

## Save result into a csv file and read the csv file to check

```{r }
write.csv(df2,"chess_game_file.csv")
csv_file<-read.csv("chess_game_file.csv")
csv_file
```




